### 2023-06-08 python_excel_ite.tex
very rough first draft

\section{Classroom experience}

>>>>

\section{Classroom experience and the future}

This module has been included in my Advanced Analytics with Python course for the past three years. The course is offered in a seven-week accelerated format during May and June. It is an online and asynchronous course. The EwP module is covered over the course of two weeks and is the subject of one of the major homework assignments for the semester. The first part of the assignment involves creating a basic model, similar in complexity to the Bookstore Model, and doing sensitivity analysis, goal seeking and simulation with the model. It requires the students to import and use the whatif.py package we created as part of the EwP module. The second part of the assignment is based on the last submodule and requires the students to complete a task involving creation of a multi-sheet Excel workbook from a set of csv files using Python. Then, using the openpyxl library, they have to create and add formulas to the workbook and format them properly. The ranges used in the formulas vary by sheet and require the students to determine the number of rows in each sheet of data and use that information to construct the appropriate formula. An example assignment is available from \href{}{here}. The module has been well received and several of the working students have reported back to me that they have found use cases for these techniques in their day to day analytical activities.

Rumours have swirled for a number of years that Microsoft was considering adding Python as a first class language alternative to VBA with their MS Office suite of packages. While this has not yet materialized, there continues to be significant interest in using Python to manipulate not only Excel workbooks but other office documents such as Powerpoint presentations. Given that business students are very familiar with both Excel and Powerpoint, inclusion of this material in a business school Python based analytics course seems quite appropriate. Students can learn more advanced and extremely useful Python concepts and techniques within a context with which they are intimately familiar. It is directly relevant to the job content of many of the students. This teaching module is a natural follow up to the commonly taught spreadsheet based analytics courses found in many business schools and provides an interesting way to teach and learn Python for analytics.
